Visualize ukb whole genome, s40.22

### 2020-10-30 analysis/index.Rmd
wg susieI
small pvalues
filtered samples s40.22
log bayes factor

## mr.ash + SUSIE iterative
*  [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-susieI-ukbchr17to22-gtex.adipose.html) 
  *  [Using UKbiobank data (chr17:22), fusion weights Adipose, test prior's effect for susie](simulation-multi-ukbchr17to22-gtex.adipose_susieprior.html)

>>>>

## SUSIE iterative
*  [Using UKbiobank data (chr17:22), fusion weights Adipose](simulation-susieI-ukbchr17to22-gtex.adipose.html) 
  *  [Using UKbiobank data (chr17:22), fusion weights Adipose, test prior's effect for susie](simulation-multi-ukbchr17to22-gtex.adipose_susieprior.html)

* [Using UKbiobank data (whole genome), fusion weights Adipose](simulation-susieI-ukbWG-gtex.adipose_s40.22.html) 
  * [Visualization](simulation-susieI-ukbWG-gtex.adipose_visual.html)

### 2020-10-30 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
qqplot
log bayes factor

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F, warning = F)
```
```{r libs}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```

@@

cat("number of genes p < 1e-5:", nrow(a[a$PVALUE < 1e-5,]))

@@

* Susie run parameters: `L=2`.  We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

```{r param1, fig.height=6, fig.width=6}
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20201001/L=2/"
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.susieI.txt")

@@

* Susie run parameters: `L=2`. We initialize with prior for genes and SNPs using their true values. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

@@

* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

## Regions: filtered (1)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.05, round 700 regions left.
* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

## Regions: filtered (2)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.01, round 400 regions left.
* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F, warning = F)
```
```{r libs}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
source("analysis/summarize_twas_plots.R")
```

@@

cat("number of genes p < 1e-5:", nrow(a[a$PVALUE < 1e-5,]))
cat("number of causal genes p < 1e-5:", nrow(a[a$PVALUE < 1e-5 & a$ifcausal ==1 ,]))

@@

* Susie run parameters: `L=1`.  We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

```{r param1, fig.height=6, fig.width=6}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.SERIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.SERI.txt")

@@

* Susie run parameters: `L=1`. We initialize with prior for genes and SNPs using their true values. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

@@

* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

## Regions: filtered (1)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.05, round 700 regions left.
* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

## Regions: filtered (2)
* We filterd regions with regional minimum FDR of both genes and SNPs < 0.01, round 400 regions left.
* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.

@@

# Plot PIP

Red is causal.

```{r gene twas, fig.height=4, fig.width=10}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config2.1.SERI.txt")
a <- fread(pipfile, header = T)

plot(a[a$chr ==chrom, ]$pos, a[a$chr ==chrom, ]$SERpip, col = a[a$chr ==chrom, ]$ifcausal + 1, xlab = paste0("chr", chrom), ylab = "pip", pch = c(1,2)[as.factor(a[a$chr ==chrom, ]$type)])
points(a[a$chr ==chrom & a$ifcausal ==1, ]$pos, a[a$chr ==chrom & a$ifcausal ==1, ]$SERpip , col = "red", pch = c(19, 17)[as.factor(a[a$chr ==chrom & a$ifcausal ==1 , ]$type)])
legend("topright",c("gene","SNP"),cex=.8,pch=c(1,2))
grid()
```

### 2020-10-30 analysis/simulation-susieI-ukbWG-gtex.adipose_visual.Rmd
log bayes factor

---
title: "Test mr.ash2s on ukbiobank data, chr1-22, 40k"
date: "`r Sys.Date()`"
output: html_document
---

@@

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20201001/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20201001/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20201001/"
```

```{r source file}
source("analysis/visual_twas_plots.R")
```

@@

```{r sim 1-4, out.width = "98%", out.height="95%"}
tag <- "20201001-1-4"
f <- get_files(tag= tag, tag2 = tag2)
param <- read.table(f$par, header = T, row.names = 1)
print(param)
```
```{r 1-4-17, out.width = "98%", out.height="95%"}
chrom <- "17"
cat("simulation run: ", tag, "-", tag2, "; chr: ", chrom)
plot_all(f$gmrash, f$ggwas, f$smrash, f$sgwas, f$gsusie, f$ssusie, f$rsq, chrom = chrom)
```

>>>>

---
title: "Visualize ukb whole genome, s40.22"
date: "`r Sys.Date()`"
output: html_document
---

@@

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20201001/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20201001/"

source("analysis/visual_twas_plots.R")
```

```{r functions file}

plot_all <- function(SERf, phenof, chrom, ldres = NULL){
  a <- fread(SERf , header =T)
  load(phenof)

  a <- a[a$chr == chrom,]

  if (!is.null(ldres)){
    ld <- read.table(ldres, header =T)
    a <- merge(a, ld, by = "name", all.x = T)}

  a <- a[, ifcausal:=as.character(ifcausal)]
  a[a$ifcausal == "1", "ifcausal"] = "Causal"
  a[a$ifcausal == "0", "ifcausal"] = "Non causal"

  colnames(a)[colnames(a) == "SERpip"] <-  "susiePIP"
  colnames(a)[colnames(a) == "pos"] <-  "p0"

  a[, "PVALUE"] <- -log10(a[, "pvalue"])

  dt.gene <- a[a$type == "gene", ]
  dt.snp <- a[a$type == "SNP", ]

  fig1 <- plot_susie_pip(dt.gene) 
  #fig2 <- plot_beta(dt.gene)
  fig3 <- plot_p(dt.gene)

  fig4 <- plot_susie_pip(dt.snp)
  #fig5 <- plot_beta(dt.snp) 
  fig6 <- plot_p(dt.snp) %>% layout( plot_bgcolor='#EFF6FC')

  # fig <- subplot(fig1, fig2, fig3, fig4, fig5, fig6, nrows=6, shareX = T, titleY = T)

  fig <- subplot(fig1, fig3, fig4, fig6, nrows=4, shareX = T, titleY = T)

  fig <- fig %>% layout(autosize = F, width = 600, height = 600, margin = 0.02,
                        xaxis = list(title = "Genomic position"))

  fig <- fig %>% toWebGL()
  fig
}
```

@@

first two rows are for genes, last two rows are for SNPs.

```{r sim 2-1-1, out.width = "98%", out.height="95%"}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config2.1.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```
